---
title: "Influencing Factors on Social Network Evolution"
author-inputfile: "anonauthors.tex" 
abstract: |
  The abstract should briefly summarize the contents of the paper in 150--250 words.
keywords: "First keyword \\and Second keyword \\and Another keyword."
bibliography: ["rpackages.bib", "bibliography.bib"]
biblio-style: "apalike"
link-citations: true
output:
  pdf_document:
    fig_caption: true
    keep_tex: true
    template: lncs-template.tex
    md_extensions: +footnotes
    citation_package: biblatex
    dev: pdf
    
---


```{r knitr_init, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, paged.print=TRUE}
## Global options
library(knitr)
#options(max.print="75")
opts_chunk$set(echo=FALSE,
	             cache=FALSE,
               prompt=FALSE,
               tidy=TRUE,
               comment=NA,
               message=FALSE,
               warning=FALSE,
               out.width='100%'
               )
opts_knit$set(width=100)

# Load required libraries
library(rmdformats)
library(tidyverse)
library(cowplot)
# add libraries here

# Add libraries to cite here:
pkgs <- c("knitr", "tidyverse", "rmdformats", "kableExtra", "scales", "psych", "rmdtemplates")
rmdtemplates::write_bib(pkgs)
```


# Introduction
In the past decade the evolution of the internet and social media platforms rised new forms of social networks that changed our interpersonal communication and the methods of information procurement considerably. It has become very easy to connect to existing friends online, look for new friends and exchange information with them. As the formation of an individual's opinion is based on all available resources it is important to understand how the information received in online social networks is embedded and how people behave in such networks. 

# Theory
Existing research states that the vast availability of similar-minded people in online social networks leads us to enclose ourselves in so-called echo chambers and to disconnect from people who are too different from us. This leads us to reinforce our opinion solely through 

We wanted to simulate such behavior in an agent-based model to be able to understand the crucial factors in the dynamics of online social networks.


# First Section
## A Subsection Sample
Please note that the first paragraph of a section or subsection is
not indented. The first paragraph that follows a table, figure,
equation etc. does not need an indent, either.

Subsequent paragraphs, however, are indented.

### Sample Heading (Third Level) 
Only two levels of
headings should be numbered. Lower level headings remain unnumbered;
they are formatted as run-in headings.

#### Sample Heading (Fourth Level)
The contribution should contain no more than four levels of
headings. Table \ref{tab1} gives a summary of all heading levels.

Another nice feature are shortcuts for \eg and \ie 

# References
You can cite any paper in parenthesis as following [@valdez2017priming] or inline saying that @valdez2017priming found something.
Multiple citations are possible as well [@valdez2017priming;@valdez2019users].

You can refer to other sections by kebab-casing to section \ref{a-subsection-sample}. You can easily cite an r-package directly in the text by using the `cite_pkg` function from the package `r rmdtemplates::cite_pkg("rmdtemplates")`. 


# Environments

The environments 'definition', 'lemma', 'proposition', 'corollary', 'remark', and 'example' are defined in the LLNCS document class as well.


## Theorems
\begin{theorem}
This is a sample theorem. The run-in heading is set in bold, while
the following text appears in italics. Definitions, lemmas,
propositions, and corollaries are styled the same way.
\end{theorem}

## Equations
\begin{equation}
x + y = z
\end{equation}



## Tables
You can get the non breaking space in RStudio by pressing ALT+SPACE.
You can refer to tables by using Table \ref{tab:table_1}.

```{r table_1, echo=FALSE}
# Note that the label has to be added manually in the caption here.
iris %>% head() %>% knitr::kable(caption = "Test\\label{tab:table_1}")
```


### Inline Latex Tables
You can directly add latex tables.

\begin{table}
\caption{Table captions should be placed above the
tables.}\label{tab1}
\begin{tabular}{|l|l|l|}
\hline
Heading level &  Example & Font size and style\\
\hline
Title (centered) &  {\Large\bfseries Lecture Notes} & 14 point, bold\\
1st-level heading &  {\large\bfseries 1 Introduction} & 12 point, bold\\
2nd-level heading & {\bfseries 2.1 Printing Area} & 10 point, bold\\
3rd-level heading & {\bfseries Run-in Heading in Bold.} Text follows & 10 point, bold\\
4th-level heading & {\itshape Lowest Level Heading.} Text follows & 10 point, italic\\
\hline
\end{tabular}
\end{table}


## Figures

You can refer to tables by using Figure \ref{fig:fig1}.

```{r fig1, fig.cap="This is the text caption under the figure"}
# Note that the label for a figure is always fig:chunkname
iris %>% ggplot() + aes(x = Sepal.Length) + geom_histogram() + cowplot::theme_minimal_hgrid()

```



# Acknowledgements {-}
We would like to thank xyz.
We would further like to thank the authors of the packages we have used.
```{r r_citations, eval=TRUE, include=TRUE, results="asis"}
rmdtemplates::line_cite(pkgs) # This creates a single line citing all packages
#rmdtemplates::list_cite(pkgs) # This creates a "thightlist" of all packages 
```

# References
